---
title: "Resubmission"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(NetBlotch)
library(parallel)
library(tidyr)
library(dplyr)
library(ggplot2)
library(ggthemes) # Using this to add extra lines to facet_wrap graphs
library(ggpubr)
library(gridExtra)
library(ggh4x)

RESIM = TRUE # Flag - whether to resimulate all the results
SAVE = TRUE # Flag - whether to save figures or not

```

## Introduction

This document includes code to reproduce the figures in Helps (2023 hopefully, in press).

## Model / methods

### Parameterisation

The following gives the default parameterisation used for each case in the papers. The default parameters can therefore be obtained by running `par <- default_par(20)` if you want to simulate 20 years.

```{r default_parameters}

default_par<-function(n_years = 50){
  p <- parameters()
  f1 = data.frame(
    Fungicide = c(2,1,3),
    Dose = 1,
    Time = c(0,400,700)
  )
  f2 = data.frame(
    Fungicide = c(3,1,3),
    Dose = 1,
    Time = c(0,400,700)
  )
  f3 = data.frame(
    Fungicide = c(3,3,3),
    Dose = 1,
    Time = c(0,400,700)
  )
  mngmt = create_management(field1 = f1, field2 = f2, field3 = f3,n_years = n_years)
  p$management = mngmt
  p$n_years = n_years
  p
}

```

### Tests

These two tests just check that resistance develops to each fungicide.

Firstly, to the azole:

```{r test_azole_res}

parms <- default_par()
parms$n_years = 20
parms$field_size = c(0.8,0.1,0.1)
f1 = data.frame(Field = 1,Fungicide = 1,Year = 1,Time = c(400,700),Dose = 1)
parms$management = create_management(f1,n_years = parms$n_years)
sim <- parms |> simulate()
sf <- sim |> calculate_strain_frequency()

ggplot(subset(sf,DD == 1200),aes(x=time,y=100 * Freq,color = factor(Strain))) +
   geom_line() +
   labs(x="Time (years)",y="Frequency (%)",color="Strain") +
   facet_wrap(~Field)

```

Or if we just spray the SHDI:

```{r test_SDHI_res}

parms <- default_par()
parms$n_years = 20
parms$field_size = c(0.9,0.05,0.05)
parms$management = data.frame(Field = 1,Fungicide = 2,Year = seq_len(parms$n_years),Time = 600,Dose = 1)
sim <- parms |> simulate()
sf <- sim |> calculate_strain_frequency()

ggplot(subset(sf,DD == 1200),aes(x=time,y=Freq,color = factor(Strain))) +
   geom_line() +
   labs(x="Time (years)",y="Frequency (%)",color="Strain") +
   facet_wrap(~Field)

```

### Figure 3

```{r figure_3}

# HAI over time, with data
LAI_data = data.frame(DegreeDay = seq(0,1200,100),
                 NinetyFour = c(0.01,0.02,0.06,0.2,0.36,0.5,0.699,0.9,1.0,0.8,0.6999,0.4,0.2),
                 NinetyFive = c(0.0,0.0,0.045,0.364,0.318,0.5,0.864,0.591,1.0,0.864,0.773,0.682,0.0364))
parms <- default_par()
parms$transmission_rate = 0.0
parms$n_years = 1
abc = simulate(parms)
fig3.1 <- ggplot(abc,aes(x=DD,y=H.F1 / (max(H.F1)+0.1))) + 
  geom_line() +
  theme_classic() + 
  geom_point(data=LAI_data,aes(x=DegreeDay,y=NinetyFour,shape=as.factor(1994))) +
  geom_point(data=LAI_data,aes(x=DegreeDay,y=NinetyFive,shape=as.factor(1995))) +
  theme(legend.position = "none") +
  labs(y="Relative healthy area index",x="Time (degree days)",shape="Observations:",linetype="Simulation:")

# Severity over time
severity_data = data.frame(GS = c(31,33,55,85,55,65,75,85,45,60,90,25,35,45,59,69,73,83),
                           sev = c(14.25,15,18.75,35.6,15.4,17.9,30,49.1,7.45,20.8,39.2,2,8,14,15.2,21.2,30,36.8),
                           thermal_time = c(341,363,605,935,605,715,825,935,495,660,990,275,385,495,649,759,803,913),
                           rep = c(1,1,1,1,2,2,2,2,3,3,3,4,4,4,4,4,4,4))
parms <- default_par()
parms$n_years = 1
parms$management = data.frame(Field=numeric(),Fungicide = numeric(),Year=numeric(),Time=numeric(),Dose=numeric())
abc = simulate(parms) |> 
   calculate_severity()
fig3.2 <- ggplot(abc,aes(x=DD,y=100*field.1)) + 
   geom_line() +
   theme_classic() +
   geom_point(data=severity_data,aes(x=thermal_time,y=sev)) +
   theme(legend.position = "none") +
   labs(x="Time (degree days)",y="Severity (%)")

# Dose-response curves
dose = seq(0,1,0.1)
dr_curve = expand.grid(Fung = 1:3,Res = c(1,2),Dose = dose,Case = c(1,2))
dr_curve$sev = NA
for(i in 1:nrow(dr_curve)){
   parms = default_par()
   if(dr_curve$Case[i] == 2){
      parms$dose_response_asymptote[2,c(1,2)] = 0.5
      parms$dose_response_asymptote[3,] = 0.3
   }
   parms$n_years = 1
   parms$management = data.frame(Field = 1,Fungicide = dr_curve$Fung[i],Year = 1,Time = 700,Dose = dr_curve$Dose[i])
   parms$initial_resistance_frequency = rep(ifelse(dr_curve$Res[i] == 1,0,1),2)
   sim<-parms |> simulate() |> calculate_severity()
   dr_curve$sev[i] = sim$field.1[1001]
}
dr_curve$Fung = factor(c("Azole","SDHI","Multi-site")[dr_curve$Fung],levels=c("Azole","SDHI","Multi-site"))
dr_curve$Res = factor(c("S","R")[dr_curve$Res],levels=c("S","R"))
dr_curve$Case = factor(dr_curve$Case)

dr_curve_2 <- dr_curve |> 
  group_by(Fung,Res,Case) |> 
  mutate(rel_sev = sev / sev[Dose==0]) |> 
  ungroup()

propiconazole_data = data.frame(Dose = c(0,0.25,0.5,1.0,2.0),
                           rel_sev.S = c(1,0.7033,0.501,0.270,0.279),
                           rel_sev.R = c(1,1.05,0.910,0.933,0.85))
fig3.3 <- ggplot(subset(dr_curve_2,Fung=="Azole" & Case == 1),aes(x=Dose,y=rel_sev,linetype=Res)) +
   geom_line() +
   geom_point(data=propiconazole_data,aes(x=Dose,y=rel_sev.S,linetype="S")) +
   geom_point(data=propiconazole_data,aes(x=Dose,y=rel_sev.R,linetype="R")) +
  theme_classic() +
   scale_y_continuous(limits = c(0,1)) +
   scale_x_continuous(limits = c(0,1)) +
   labs(y="Relative severity") +
   theme(legend.position="none")

fluxapyroxad_data = data.frame(Dose = c(0,0.25,0.5,1.0),
                          sev_2012 = c(1.0,0.04,0.1,0.1),
                          sev_2013 = c(1.0,0.15,0.08,0.06),
                          sev_2014 = c(1.0,0.36,0.18,0.09),
                          sim = rep(NA,4))
fig3.4 <- ggplot(subset(dr_curve_2,Fung=="SDHI"),aes(x=Dose,y=rel_sev,linetype=Res,colour=Case)) +
   geom_line() +
   geom_line(data = subset(dr_curve_2,Fung=="SDHI" & Case == 1 & Res == "R"),aes(x=Dose,y=rel_sev)) +
   geom_point(data=fluxapyroxad_data,aes(x=Dose,y=sev_2012,linetype="S"),col=1) +
   geom_point(data=fluxapyroxad_data,aes(x=Dose,y=sev_2013,linetype="S"),col=1) +
   geom_point(data=fluxapyroxad_data,aes(x=Dose,y=sev_2014,linetype="S"),col=1) +
   theme_classic() +
   scale_y_continuous(limits = c(0,1)) +
   scale_color_discrete(type = c("black","red")) +
   labs(y="Relative severity") +
   theme(legend.position="none")

fig3.5 <- ggplot(subset(dr_curve_2,Fung=="Multi-site"),aes(x=Dose,y=rel_sev,linetype=Res,col=Case)) +
   geom_line() +
   theme_classic() +
   scale_y_continuous(limits = c(0,1)) +
   scale_color_discrete(type = c("black","red")) +
   labs(y="Relative severity") +
   theme(legend.position="none")

```

```{r seed_treatments}

for(fung_i in 1:3){
   
   # Seed treatment - two fields, one with seed treatment, one with foliar applied spray
   parms <- default_par()
   parms$seed_treatment_coefficient = c(0.95,0.25,1.2) # Use the new coefficients
   parms$n_fields = 3
   parms$n_years = 1
   parms$field_size = c(0.5,0.25,0.25)
   parms$management = subset(parms$management,Field<3 & Fungicide == 1 & Year ==1)
   parms$management$Time[1] = 600
   parms$management$Time[2] = 0
   parms$management$Fungicide = fung_i
   parms$initial_resistance_frequency = c(0,0)
   parms$mutation_rate = 0.0
   
   sim <- simulate(parms) |> 
      calculate_severity() |> 
      pivot_longer(cols = starts_with("field"),names_to="Treatment",names_prefix="field.",values_to="sev")
   
   sim$Treatment[sim$Treatment == 1] = "Foliar"
   sim$Treatment[sim$Treatment == 2] = "Seed"
   sim$Treatment[sim$Treatment==3] = "No control"
   sim$Treatment = factor(sim$Treatment,levels=c("No control","Foliar","Seed"))
   
   sim <- cbind(sim,Fung=fung_i)
   
   if(fung_i == 1){
      st_foliar <- sim
   } else st_foliar <- rbind(st_foliar,sim)
   
}

fig3.6<- ggplot(subset(st_foliar,Fung==3),aes(x=time,y=100*sev,linetype=Treatment)) +
   geom_line() +
   labs(x="Time (degree days)",y="Severity (%)",linetype="Treatment:",colour="Fungicide:") +
   theme_classic() +
   geom_vline(xintercept = 1 + 1000 / 1200) +
   scale_y_continuous(limits=c(0,100)) +
   #theme(legend.position="none")
   theme(legend.position=c(.4,.75))

```

```{r fig3}

plot3 <- ggarrange(fig3.1 + labs(tag="A"),
                   fig3.2 + labs(tag="B"),
                   fig3.6 + labs(tag="C"),
                   fig3.3 + labs(tag="D") + ggtitle("Propiconazole"),
                   fig3.4 + labs(tag="E") + ggtitle("Fluxapyroxad"),
                   fig3.5 + labs(tag="F") + ggtitle("Third fungicide"))

if(SAVE) ggsave("fig3.png",plot3,width=7,height=5)

```

### Figure 4

Figure 4 plots the disease progress curves in four situations.

1. No sprays
2. A single foliar application at T2
3. Foliar sprays at T1 and T2
4. Seed treatment, and foliar sprays at T1 and T2.

```{r figure_4}

fig4_sim <- data.frame()

# HLIR with no sprays
par = default_par()
par$management = data.frame(Field=numeric(),Fungicide = numeric(),Year=numeric(),Time=numeric(),Dose=numeric())
par$n_years = 1
abc = simulate(par) |> calculate_SLIR() |> group_by(Field) |> pivot_longer(cols = !c(1,2,3,4),names_to = "State")
fig4.1 <- ggplot(subset(abc,Field==1),aes(x=time,y=value,col=State)) + 
  geom_line(size = 1) +
  ggtitle("No sprays") +
   labs(y="Area index",x="Time (degree days)") +
   #scale_y_continuous(limits = c(0,2.5)) +
   theme_classic() +
   theme(axis.text.x = element_blank())

# HLIR with 1 spray at T2
par = default_par()
par$management = data.frame(Field=1,Fungicide = 1,Year=1,Time=700,Dose=1)
par$n_years = 1
abc = simulate(par) |> calculate_SLIR() |> pivot_longer(cols = !c(1,2,3,4),names_to = "State")
fig4.2 <- ggplot(subset(abc,Field==1),aes(x=time,y=value,col=State)) + 
  geom_line(size = 1) +
  ggtitle("Spray at T2") +
  labs(y="Area index",x="Time (degree days)") +
  #scale_y_continuous(limits = c(0,2.5)) +
  theme_classic() +
  theme(axis.text.x = element_blank())

# HLIR with 2 sprays at T1 and T2
par = default_par()
par$management = data.frame(Field=1,Fungicide = 1,Year=1,Time=c(400,700),Dose=1)
par$n_years = 1
abc = simulate(par) |> calculate_SLIR() |> pivot_longer(cols = !c(1,2,3,4),names_to = "State")
fig4.3 <- ggplot(subset(abc,Field==1),aes(x=time,y=value,col=State)) + 
  geom_line(size = 1) +
  ggtitle("Sprays at T1 & T2") +
  labs(y="Area index",x="Time (degree days)") +
  #scale_y_continuous(limits = c(0,2.5)) +
  theme_classic() +
  theme(axis.text.x = element_blank())

# HLIR with 3 sprays (T0, T1, T2)
par = default_par()
par$management = data.frame(Field=1,Fungicide = 1,Year=1,Time=c(0,400,700),Dose=1)
par$n_years = 1
abc = simulate(par) |> calculate_SLIR() |> pivot_longer(cols = !c(1,2,3,4),names_to = "State")
fig4.4 <- ggplot(subset(abc,Field==1),aes(x=time,y=value,col=State)) + 
  geom_line(size = 1) +
  ggtitle("Seed treatment, T1 & T2") +
  labs(y="Area index",x="Time (degree days)") +
  #scale_y_continuous(limits = c(0,2.5)) +
  theme_classic() +
  theme(
  axis.text.x = element_blank(),
  axis.line = element_line(),)

plot4 <- ggarrange(fig4.1 + labs(tag="A"),
                   fig4.2 + labs(tag="B"),
                   fig4.3 + labs(tag="C"),
                   fig4.4 + labs(tag="D"),
                   common.legend=TRUE,legend="right")

if(SAVE) ggsave("fig4.png",plot4,width=6,height=4)

```

## Results

### Case 1

In Case 1, control is ineffective only when resistance develops to both fungicide MOAs.

I first plot the HADs, to show the HAD in each case when resistance has developed to none, one, or both mode of actions (MOAs).

```{r HAD_0}

pars <- default_par()
pars$n_years = 1
pars$transmission_rate = 0.0

HAD_0 = pars |> simulate() |> calculate_HAD()
HAD_0 = HAD_0$field.1[1]

```

```{r HADs}

HADs = data.frame(Field = rep(seq(5),each=4),Exp = rep(seq(4),times=5),HAD=NA)

params = default_par()
params$n_years = 1

for(i in 1:nrow(HADs)){
  
  if(HADs$Field[i] == 1){
    # Field 1
    params$management = data.frame(Field = 1,Fungicide = c(2,1,3),Year=1,Time = c(0,400,700),Dose=1)
  } else if(HADs$Field[i] == 2){
    # Field 1 - mixture
    params$management = data.frame(Field = 1,Fungicide = c(3,1,2,3),Year=1,Time = c(0,400,400,700),Dose=c(1,0.5,0.5,1))
  } else if(HADs$Field[i] == 3){
    # Field 2 - azole
    params$management = data.frame(Field = 1,Fungicide = c(3,1,3),Year=1,Time = c(0,400,700),Dose=1)
  } else if(HADs$Field[i] == 4){
    # Field 2 - SDHI
    params$management = data.frame(Field = 1,Fungicide = c(2,3,3),Year=1,Time = c(0,400,700),Dose=1)
  } else if(HADs$Field[i] == 5){
    # Field 3
    params$management = data.frame(Field = 1,Fungicide = c(3,3,3),Year=1,Time = c(0,400,700),Dose=1)
  }
  
  if(HADs$Exp[i] == 1){
    params$initial_resistance_frequency = c(0,0)
  } else if(HADs$Exp[i] == 2){
    params$initial_resistance_frequency = c(1,0)
  } else if(HADs$Exp[i] == 3){
    params$initial_resistance_frequency = c(0,1)
  } else if(HADs$Exp[i] == 4){
    params$initial_resistance_frequency = c(1,1)
  }
  
  tmp = params |> simulate() |> calculate_HAD()
  HADs$HAD[i] = tmp[1,2]
}

HADs$Field = factor(rep(c("1 - alt","1 - mix","2 - azole","2 - SDHI","3"),each=4))
HADs$Exp = factor(rep(c("Susceptible","Resistant to azole","Resistant to SDHI","Resistant to both"),times=5),
                  levels = c("Susceptible","Resistant to azole","Resistant to SDHI","Resistant to both"))

HADs_C1 <- 
   ggplot(HADs,aes(fill=factor(Exp),y=HAD,x=Field)) +
     geom_bar(position="dodge",stat="identity") +
     theme_light() +
     geom_hline(yintercept=HAD_0) + geom_hline(yintercept=HAD_0 * 0.9,linetype=2) +
     labs(y="HAD",fill="Resistance:",x="Field")

if(SAVE) ggsave(filename="HAD_C1.png",HADs_C1,width=7,height=3)

```

Figure. The HAD under each spray programme in the landscape when the pathogen population is either susceptible, resistant to the azole, resistant to the SDHI, or resistant to both MoAs. From left to right, each block is: Field 1, with an alternation; Field 1 with a mixture; Field 2 with an azole; Field 2 with an SDHI; Field 3. For details of the spray programmes, see Table 2 in the main paper.

We can now calculate the effective life under different proportions of field 2.

```{r figure_5}

if(RESIM){

   figure5<-expand.grid(
      Strategy = c("Mixture","Alternation"),
      Field2 = c("Azole","SDHI"),
      sex_prop = c(0,0.5,1),
      disp = c(0.2,0.5,1.0),
      p_field_2 = seq(0,0.5,0.05),
      EL=NA)
   
   cl <- makeCluster(detectCores()-1)
   clusterEvalQ(cl,library(NetBlotch))
   clusterExport(cl,c("figure5","default_par","HAD_0","create_management"))
   figure5$EL = parSapply(cl,seq_len(nrow(figure5)),function(x) {
     
     par = default_par()
     
     if(figure5$Strategy[x] == "Mixture"){
       n_years = par$n_years
       par$management$Fungicide[par$management$Field == 1] = 3
       par$management$Fungicide[par$management$Field == 1 & par$management$Time == 400] = 2
       par$management$Dose[par$management$Field == 1 & par$management$Time == 400] = 0.5
       par$management = rbind(par$management,data.frame(Field=1,Fungicide=1,Year=seq_len(n_years),Time=400,Dose=0.5))
     }
     
     if(figure5$Field2[x] == "SDHI"){
         par$management$Fungicide[par$management$Field == 2] = 3
         par$management$Fungicide[par$management$Field == 2 & par$management$Time == 0] = 2
     }
     
     par$sex_prop = figure5$sex_prop[x]
     par$overwinter_dispersal_proportion = figure5$disp[x]
     par$field_size[2] = figure5$p_field_2[x]
     par$field_size[3] = 0.5 - figure5$p_field_2[x]
     
     EL <- simulate(par) |> calculate_effective_life(max_HAD = HAD_0,threshold=10)
     EL[1]
     
   })
   stopCluster(cl)
   
} else figure5 = read.csv("./figure5.csv")

plot5 <- 
   ggplot(figure5,aes(x=p_field_2,y=EL,linetype=factor(disp))) +
      geom_line() +
      facet_nested(sex_prop ~ Strategy + Field2) +
      labs(x="Proportion field 2",y="Effective life",colour = "Sex prop.",linetype="Dispersal prop.") +
      coord_cartesian(ylim=c(0,50)) +
      theme_classic()+
      theme(panel.border = element_rect(colour = "black", fill=NA, linewidth=1))

if(SAVE) ggsave("fig5.png",plot5,width=7,height=5)

if(RESIM) write.csv(figure5,file="figure5.csv")

```

### Case 2

In Case 2, control is ineffective when resistance develops to either of the fungicide MOAs.

```{r HADs_case2}

HADs_2 = data.frame(Field = rep(seq(5),each=4),Exp = rep(seq(4),times=5),HAD=NA)

params = default_par()
params$dose_response_asymptote[2,c(1,2)] = 0.5
params$dose_response_asymptote[3,] = 0.3
params$n_years = 1

for(i in 1:nrow(HADs_2)){
  
  if(HADs_2$Field[i] == 1){
    # Field 1
    params$management = data.frame(Field = 1,Fungicide = c(2,1,3),Year=1,Time = c(0,400,700),Dose=1)
  } else if(HADs_2$Field[i] == 2){
    # Field 1 - mixture
    params$management = data.frame(Field = 1,Fungicide = c(3,1,2,3),Year=1,Time = c(0,400,400,700),Dose=c(1,0.5,0.5,1))
  } else if(HADs_2$Field[i] == 3){
    # Field 2 - azole
    params$management = data.frame(Field = 1,Fungicide = c(3,1,3),Year=1,Time = c(0,400,700),Dose=1)
  } else if(HADs_2$Field[i] == 4){
    # Field 2 - SDHI
    params$management = data.frame(Field = 1,Fungicide = c(2,3,3),Year=1,Time = c(0,400,700),Dose=1)
  } else if(HADs_2$Field[i] == 5){
    # Field 3
    params$management = data.frame(Field = 1,Fungicide = c(3,3,3),Year=1,Time = c(0,400,700),Dose=1)
  }
  
  if(HADs_2$Exp[i] == 1){
    params$initial_resistance_frequency = c(0,0)
  } else if(HADs_2$Exp[i] == 2){
    params$initial_resistance_frequency = c(1,0)
  } else if(HADs_2$Exp[i] == 3){
    params$initial_resistance_frequency = c(0,1)
  } else if(HADs_2$Exp[i] == 4){
    params$initial_resistance_frequency = c(1,1)
  }
  
  tmp = params |> simulate() |> calculate_HAD()
  HADs_2$HAD[i] = tmp[1,2]
  
}

HADs_2$Field = factor(rep(c("1 - alt","1 - mix","2 - azole","2 - SDHI","3"),each=4))
HADs_2$Exp = factor(rep(c("Susceptible","Resistant to azole","Resistant to SDHI","Resistant to both"),times=5),
                  levels = c("Susceptible","Resistant to azole","Resistant to SDHI","Resistant to both"))

HAD_C2 <- 
   ggplot(HADs_2,aes(fill=factor(Exp),y=HAD,x=Field)) +
     geom_bar(position="dodge",stat="identity") +
     theme_light() +
     geom_hline(yintercept=HAD_0) + geom_hline(yintercept=HAD_0 * 0.9,linetype=2) +
     labs(y="HAD",fill="Resistance:",x="Field")

if(SAVE) ggsave(filename="HAD_C2.png",HAD_C2,width=7,height=3)

```

Figure. The HAD under each spray programme in the landscape when the pathogen population is either susceptible, resistant to the azole, resistant to the SDHI, or resistant to both MoAs. From left to right, each block is: Field 1, with an alternation; Field 1 with a mixture; Field 2 with an azole; Field 2 with an SDHI; Field 3. For details of the spray programmes, see Table 2 in the main paper.

```{r figure_6}

if(RESIM){

   figure6<-expand.grid(
      Strategy = c("Mixture","Alternation"),
      Field2 = c("Azole","SDHI"),
      sex_prop = c(0,0.5,1),
      disp = c(0.2,0.5,1.0),
      p_field_2 = seq(0,0.5,0.05),
      EL=NA)
   
   cl <- makeCluster(detectCores()-1)
   clusterEvalQ(cl,library(NetBlotch))
   clusterExport(cl,c("figure6","default_par","HAD_0"))
   figure6$EL = parSapply(cl,seq_len(nrow(figure6)),function(x) {
     
     par = default_par()
     par$dose_response_asymptote[2,c(1,2)] = 0.5
     par$dose_response_asymptote[3,] = 0.3
     
     if(figure6$Strategy[x] == "Mixture"){
        n_years = par$n_years
        par$management$Fungicide[par$management$Field == 1] = 3
        par$management$Fungicide[par$management$Field == 1 & par$management$Time == 400] = 2
        par$management$Dose[par$management$Field == 1 & par$management$Time == 400] = 0.5
        par$management = rbind(par$management,data.frame(Field=1,Fungicide=1,Year=seq_len(n_years),Time=400,Dose=0.5))
     }
     
     if(figure6$Field2[x] == "SDHI"){
         par$management$Fungicide[par$management$Field == 2] = 3
         par$management$Fungicide[par$management$Field == 2 & par$management$Time == 0] = 2
     }
     
     par$sex_prop = figure6$sex_prop[x]
     par$overwinter_dispersal_proportion = figure6$disp[x]
     par$field_size[2] = figure6$p_field_2[x]
     par$field_size[3] = 0.5 - figure6$p_field_2[x]
     
     EL <- simulate(par) |> 
       calculate_effective_life(max_HAD = HAD_0,threshold=10)
     EL[1]
     
   })
   
   stopCluster(cl)
   
} else figure6 = read.csv("./figure6.csv")

plot6 <- 
   ggplot(figure6,aes(x=p_field_2,y=EL,linetype=factor(disp))) +
      geom_line() +
      facet_nested(sex_prop ~ Strategy + Field2) +
      labs(x="Proportion field 2",y="Effective life",colour = "Sex prop.",linetype="Dispersal prop.") +
      coord_cartesian(ylim=c(0,50)) +
      theme_classic()+
      theme(panel.border = element_rect(colour = "black", fill=NA, linewidth=1))

if(SAVE) ggsave("fig6.png",plot6,width=7,height=5)

if(RESIM) write.csv(figure6,file="figure6.csv")

```

## Explanation

The following figure plots the strain frequency over time under different scenarios.

As all cases are too complicated for the paper, several subsets were selected for the paper figure.

```{r figure7}

fig7 <- expand.grid(
   prop_field_2 = c(0,0.25,0.5),
   field_2 = c("Azole","SDHI"),
   Strat = c("Alt","Mix"),
   Case = c(1,2),
   sex = c(FALSE,TRUE))

cl<-makeCluster(detectCores()-1)

clusterExport(cl,c("fig7","default_par"))
clusterEvalQ(cl,{library(deSolve);library(NetBlotch)})

sims_fig7 = parLapply(cl,X=seq(1,nrow(fig7)),fun=function(i) {
   
   parms <- default_par()
   parms$n_years = 50
   parms$sex_prop = 0.0
   parms$overwinter_dispersal_proportion = 1.0
   parms$field_size = c(0.5,fig7$prop_field_2[i],0.5-fig7$prop_field_2[i])

   if(fig7$Case[i] == 2){
      parms$dose_response_asymptote[2,c(1,2)] = 0.5
      parms$dose_response_asymptote[3,] = 0.3
   }
   
   if(fig7$Strat[i] == "Mix"){
       n_years = parms$n_years
       parms$management$Fungicide[parms$management$Field == 1] = 3
       parms$management$Fungicide[parms$management$Field == 1 & parms$management$Time == 400] = 2
       parms$management$Dose[parms$management$Field == 1 & parms$management$Time == 400] = 0.5
       parms$management = rbind(parms$management,data.frame(Field=1,Fungicide=1,Year=seq_len(n_years),Time=400,Dose=0.5))
  }
  
  if(fig7$field_2[i] == "SDHI"){
      parms$management$Fungicide[parms$management$Field == 2] = 3
      parms$management$Fungicide[parms$management$Field == 2 & parms$management$Time == 0] = 2
  }
   
   if(fig7$sex[i] == TRUE){
    parms$sex_prop = 1.0
   }
   
   sim <- parms |> simulate() |> 
     calculate_strain_frequency() |> 
     subset(DD==1200 & Field == 1)
   
   sim
   
})

stopCluster(cl)

fig7_sims_all <- cbind(sims_fig7[[1]],fig7[1,])
for(i in 2:nrow(fig7)) fig7_sims_all <- rbind(fig7_sims_all,cbind(sims_fig7[[i]],fig7[i,]))

## Now, we want to extract the rows that Frank wants in the figure:
fig7_sims = fig7_sims_all |> subset(
  (Case == 1 & sex == FALSE & Strat == "Mix") | 
    (Case == 1 & sex == TRUE & Strat == "Alt") | 
    (Case == 2 & sex == FALSE & Strat == "Mix")
)

plot7 <- ggplot(fig7_sims,aes(x=Year,y=Freq,color=factor(Strain))) +
   geom_line() +
   facet_nested(Case + sex + Strat + field_2 ~ prop_field_2) +
   theme_classic()+
   theme(panel.border = element_rect(colour = "black", fill=NA, size=1))

if(SAVE) ggsave("fig7.png",plot7,width=7,height=5)

```

## Appendix

### Mutation rate

Reviewer 2 asked if we could test the sensitivity of our results to the mutation rate.

To do so, we looked at the effective life in a subset of the above tests, with three levels of mutation rate.

```{r figure_A1_mutation}

if(RESIM){

   figureA1<-expand.grid(
      Strategy = c("Alternation","Mixture"),
      Field2 = c("Azole","SDHI"),
      sex_prop = c(0,1),
      disp = c(0.2,0.5,1.0),
      p_field_2 = seq(0,0.5,0.1),
      mutation_rate = c(1e-7,1e-5,1e-3),
      EL=NA)
   
   cl <- makeCluster(detectCores()-1)
   clusterEvalQ(cl,library(NetBlotch))
   clusterExport(cl,c("figureA1","default_par","HAD_0","create_management"))
   figureA1$EL = parSapply(cl,seq_len(nrow(figureA1)),function(x) {
     
     par = default_par()
     
     if(figureA1$Strategy[x] == "Mixture"){
       n_years = par$n_years
       par$management$Fungicide[par$management$Field == 1] = 3
       par$management$Fungicide[par$management$Field == 1 & par$management$Time == 400] = 2
       par$management$Dose[par$management$Field == 1 & par$management$Time == 400] = 0.5
       par$management = rbind(par$management,data.frame(Field=1,Fungicide=1,Year=seq_len(n_years),Time=400,Dose=0.5))
     }
     
     if(figureA1$Field2[x] == "SDHI"){
         par$management$Fungicide[par$management$Field == 2] = 3
         par$management$Fungicide[par$management$Field == 2 & par$management$Time == 0] = 2
     }
     
     par$sex_prop = figureA1$sex_prop[x]
     par$overwinter_dispersal_proportion = figureA1$disp[x]
     par$mutation_rate = figureA1$mutation_rate[x]
     
     par$field_size[2] = figureA1$p_field_2[x]
     par$field_size[3] = 0.5 - figureA1$p_field_2[x]
     
     EL <- simulate(par) |> calculate_effective_life(max_HAD = HAD_0,threshold=10)
     EL[1]
     
   })
   stopCluster(cl)
   
} else figureA1 = read.csv("./figureA1.csv")

plotA1 <- 
   ggplot(figureA1,aes(x=p_field_2,y=EL,linetype=factor(disp))) +
      geom_line() +
      facet_nested(sex_prop ~ Strategy + Field2) +
      labs(x="Proportion field 2",y="Effective life",colour = "Sex prop.",linetype="Dispersal prop.") +
      coord_cartesian(ylim=c(0,50)) +
      theme_classic()+
      theme(panel.border = element_rect(colour = "black", fill=NA, linewidth=1))

if(SAVE) ggsave("figA1.png",plotA1,width=7,height=5)

if(RESIM) write.csv(figureA1,file="figureA1.csv")

```

### Fitness cost

Reviewer 2 also asked about an "adaptation cost", which we assume means "fitness cost".

Fitness cost implies that the fitness of resistant individuals is reduced, and we want to test this with a fitness cost on the transmission rate.

If we say that the transmission rate, $\theta = 0.1$, then we say that for those genotypes with a single resistance allele the transmission rate is reduced by $(1-\theta)$, i.e. 90%.

```{r figure_A2_fitness_cost}

if(RESIM){

   figureA2<-expand.grid(
      Strategy = c("Mixture","Alternation"),
      Field2 = c("Azole","SDHI"),
      sex_prop = c(0,1),
      disp = c(0.2,0.5,1.0),
      p_field_2 = seq(0,0.5,0.1),
      trans_fc = c(1.0,0.9,0.8),
      EL=NA)
   
   cl <- makeCluster(detectCores()-1)
   clusterEvalQ(cl,library(NetBlotch))
   clusterExport(cl,c("figureA2","default_par","HAD_0","create_management"))
   figureA2$EL = parSapply(cl,seq_len(nrow(figureA2)),function(x) {
     
     par = default_par()
     
     if(figureA2$Strategy[x] == "Mixture"){
       n_years = par$n_years
       par$management$Fungicide[par$management$Field == 1] = 3
       par$management$Fungicide[par$management$Field == 1 & par$management$Time == 400] = 2
       par$management$Dose[par$management$Field == 1 & par$management$Time == 400] = 0.5
       par$management = rbind(par$management,data.frame(Field=1,Fungicide=1,Year=seq_len(n_years),Time=400,Dose=0.5))
     }
     
     if(figureA2$Field2[x] == "SDHI"){
         par$management$Fungicide[par$management$Field == 2] = 3
         par$management$Fungicide[par$management$Field == 2 & par$management$Time == 0] = 2
     }
     
     par$sex_prop = figureA2$sex_prop[x]
     par$overwinter_dispersal_proportion = figureA2$disp[x]
     par$transmission_fitness_cost = figureA2$trans_fc[x]
     
     par$field_size[2] = figureA2$p_field_2[x]
     par$field_size[3] = 0.5 - figureA2$p_field_2[x]
     
     EL <- simulate(par) |> calculate_effective_life(max_HAD = HAD_0,threshold=10)
     EL[1]
     
   })
   stopCluster(cl)
   
} else figureA2 = read.csv("./figureA2.csv")

plotA2 <- 
   ggplot(figureA2,aes(x=p_field_2,y=EL,linetype=factor(disp))) +
      geom_line() +
      facet_nested(sex_prop ~ Strategy + Field2) +
      labs(x="Proportion field 2",y="Effective life",colour = "Sex prop.",linetype="Dispersal prop.") +
      coord_cartesian(ylim=c(0,50)) +
      theme_classic()+
      theme(panel.border = element_rect(colour = "black", fill=NA, linewidth=1))

if(SAVE) ggsave("figA2.png",plotA2,width=7,height=5)

if(RESIM) write.csv(figureA2,file="figureA2.csv")

```
